Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-17 BN_discretizer_paper.tex
Experiment part

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[round]{natbib}
\usepackage{multirow}
\usepackage{pgfplots}
\usepgfplotslibrary{groupplots}
\usepackage{tikz}
\usepackage{lscape}
\usepackage{caption}
\usepackage{siunitx}
\usepackage{booktabs}
% \usepackage[capitalize]{cleveref}
\usetikzlibrary{bayesnet}
\setcitestyle{aysep={ }} %Author-Year Separator
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CUSTOM COMMANDS

@@

\begin{algorithm}
  \label{alg:disc_two}
  \caption{Discretization of multiple continuous variables \todo{Fix label reference number}}
  \begin{algorithmic}[5]
  \Function{Discretize}{$D''$, $G$, $C$, $u_{cycle}$}
    \State
    \State $M[i] \leftarrow$ the discretization policy for the $i$th variable
    \State $n \leftarrow$ the number of variables in the Bayesian network
    \State $D^*_i \leftarrow M[i] (D_i)$, list of samples $D_i$ discretized according to $M[i]$
    \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_i \leftarrow D''_i$ if $i \notin C$
    \State $k \leftarrow median\{ |v|, v\notin C\}$
    \State
    \For {$i = 1$ to $n$}
      \If {$i \in C$}
        \State $M[i] \leftarrow$  equal-width discretization with $k$ intervals
        \State $D^*_i \leftarrow  M[i] (D''_i)$
      \EndIf
    \EndFor
    \State
    \State $cycle \leftarrow 0$
    \While {$M$ is not converged  \textbf{and} $cycle \leq u_{cycle}$}
      \State {$cycle  \leftarrow cycle  + 1$}
      \For {$j = 1$ to $|C|$}
        \State $D^*_{\backslash C(j)} \leftarrow D^*$ without $D^*_{C(j)}$.
        \State {$M[C(j)] \leftarrow $ DISCRETIZE($D_{C(j)}$,$D^*_{ \backslash C(j)}$,graph)}
        \State {$D^*_{C(j)}  \leftarrow$ $M[C(j)](D''_{C(j)})$}
      \EndFor
    \EndWhile
    \State \Return $M$
  \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
  \label{alg:structure_learn}
  \caption{ Learning a discrete-valued Bayesian network}
  \begin{algorithmic}[5]
  \Function{Learn\_DBN}{$D''$, $C$, $order$, $u_{parent}$, $C$, $u_{cycle}$}
    \State $n \leftarrow$ the number of variables in the Bayesian network
    \State $k \leftarrow median\{ \|v\|, v\notin C\}$
    \State $M[i] \leftarrow$ the discretization policy for the $i$th variable
    \State $D^*_i \leftarrow M[i] (D_i)$, list of samples $D_i$ discretized according to $M[i]$
    \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_i \leftarrow D''_i$ if $i \notin C$
    \State $G \leftarrow$ the initial edgeless graph structure
    \For {$i = 1$ to $n$}
      \If {$i \in C$}
        \State $M[i] \leftarrow$  equal-width discretization with $k$ intervals
        \State $D^*_i \leftarrow  M[i] (D''_i)$
      \EndIf
    \EndFor
    \For {$i =1$ to $n$}
      \State $P_{old} \leftarrow f(X^*_i,\Pi_{X^*_i})$: Equation \ref{eq:f_x_p}
      \State OKToProceed $\leftarrow$ \textbf{true}
      \While {OKToProceed \textbf{and} $\|\Pi_{X^*_i}\| < u_{parent}$}
        \State $Y \leftarrow$ an element from the set $order[1:i] \backslash \Pi_X$
        \State $P_{new} \leftarrow f(X^*_i,\Pi_{X^*_i} \cup Y)$
        \If {$P_{new} > P_{old}$}
          \State $P_{old} \leftarrow P_{new}$
          \State $\Pi_{X_i} \leftarrow \Pi_{X_i} \cup Y $
          \State $M \leftarrow$ {DISCRETIZE}({$D''$, $G$, $C$, $u_{cycle}$}): Algorithm \ref{alg:disc_two}
          \State $D* = M(D'')$
        \Else
          \State OKToProceed $\leftarrow$ \textbf{false}
        \EndIf
      \EndWhile
    \EndFor
    \State \Return $G$, $M$
  \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

\subsection{Auto MPG Dataset}

In this subsection, two experiments are conducted on the Auto MPG dataset from the Irvine repository \citep{Lichman:2013}.
The dataset has \num{392} instances after deleting the six instances with missing data, and eight variables.
Three variables are discrete: $B$, $G$, and $H$ with cardinality 5, 13, and 3 respectively.
Two expiriments are conducted, one with a given network structure and one in which the structure is learned.

\subsubsection{Experiment 1 on the Auto MPG dataset}

@@

Figure \ref{fig:auto_exp1_distr_1_3} compares the discretization result on continuous variables $A$ and $C$ with the raw data of Auto MPG data set. The color of discretized area shows the probability of a sample being in the discretized area. The black dots in Figure \ref{auto_exp1_distr_1_3} demonstrate the distribution of the raw data. As shown in the figure, the discretization edges and the resulting marginalized probability match the raw data well.

@@

\subsubsection{Experiment 2 on the Auto MPG dataset}

@@

Figure \ref{auto_exp2_distr_1_3} compares the edges of the learned network in Figure \ref{fig:auto_graph_2} with the raw data on variables $A$ and $C$. Again, the black dots are raw data points. Although the numbers of discretization edges of $A$ and $C$ shown in Figure \ref{fig:auto_graph_2} are less than Table \ref{table:auto_disc_table_1}, they still have a good capture of raw data distribution.

@@

In this subsection, two experiments are conducted on the Wine dataset from the Irvine repository \citep{Lichman:2013}. This dataset has 178 instances and 14 variables. Only variable $A$ is discrete-valued with cardinality number 3. Again, in the first experiment, the network structure is given. In the second experiment, the network structure is not provided.

@@

The Bayesian network in Figure \ref{fig:wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 1000 times. Table \ref{table:wine_disc_table_1} shows a comparison between the proposed method and the MDL principle discretization method. The proposed method is still better than MDL principle discretization in terms of likelihood, although the latter returns non-trivial result in this experiment. Note that the proposed method with the approximation has more intervals after discretization, thus it has a slightly better result. However, as shown in next dataset, the approximation might cut continuous variables into too many intervals. Therefore, the proposed method without the approximation should be still considered a better approach.

\begin{figure}[ht]
\centering
    \begin{tabular}{cc}
      \input{graph_wine_1}
    \end{tabular}
  \caption{K2 structure learning with prediscretization on Wine dataset}
  \label{fig:wine_graph_1}
\end{figure}

\begin{table}
\centering
\scalebox{1.0}{
\input{table_wine_1.tex}
}
\caption{Discretization result of Wine dataset based on the graph Fig. \ref{Wine_graph_1}}
\label{table:wine_disc_table_1}
\end{table}

@@

Figure \ref{fig:wine_exp2_distr} shows the discretization result on variable $E$ and $K$. The discretization edge on variable $E$ is same as the edge found by the MDL principle and the proposed method in Figure \ref{wine_exp1_distr}. This indicates that some discretization edges are robust against the network structure.

@@

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_housing_1}
    \end{tabular}
  \caption{K2 structure learning with prediscretization on Housing dataset}
  \label{Housing_graph_1}
\end{figure}

\begin{table}
\centering
\scalebox{1.0}{
\input{table_housing_1.tex}
}
\caption{Discretization result of Housing dataset based on the graph Fig. \ref{Housing_graph_1}}
\label{Housing_disc_table_1}
\end{table}

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_housing_2}
    \end{tabular}
  \caption{K2 structure learning with the proposed discretization method on Housing dataset}
  \label{Housing_graph_2}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[round]{natbib}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepgfplotslibrary{groupplots}
\usepackage{tikz}
\usepackage{lscape}
\usepackage{caption}
\usepackage{siunitx}
\usepackage{booktabs}
% \usepackage[capitalize]{cleveref}
\usetikzlibrary{bayesnet}
\setcitestyle{aysep={ }} %Author-Year Separator
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\pgfplotsset{
    jitter/.style={
        x filter/.code={\pgfmathparse{\pgfmathresult+rnd*#1}}
    },
    jitter/.default=0.1
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CUSTOM COMMANDS

@@

\begin{algorithm}
  \caption{Discretization of multiple continuous variables \todo{Fix label reference number}}
  \label{alg:disc_two}
  \begin{algorithmic}[5]
  \Function{Discretize}{$D''$, $G$, $C$, $u_{cycle}$}
    \State
    \State $M[i] \leftarrow$ the discretization policy for the $i$th variable
    \State $n \leftarrow$ the number of variables in the Bayesian network
    \State $D^*_i \leftarrow M[i] (D_i)$, list of samples $D_i$ discretized according to $M[i]$
    \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_i \leftarrow D''_i$ if $i \notin C$
    \State $k \leftarrow median\{ |v|, v\notin C\}$
    \State
    \For {$i = 1$ to $n$}
      \If {$i \in C$}
        \State $M[i] \leftarrow$  equal-width discretization with $k$ intervals
        \State $D^*_i \leftarrow  M[i] (D''_i)$
      \EndIf
    \EndFor
    \State
    \State $cycle \leftarrow 0$
    \While {$M$ is not converged  \textbf{and} $cycle \leq u_{cycle}$}
      \State {$cycle  \leftarrow cycle  + 1$}
      \For {$j = 1$ to $|C|$}
        \State $D^*_{\backslash C(j)} \leftarrow D^*$ without $D^*_{C(j)}$.
        \State {$M[C(j)] \leftarrow $ DISCRETIZE($D_{C(j)}$,$D^*_{ \backslash C(j)}$,graph)}
        \State {$D^*_{C(j)}  \leftarrow$ $M[C(j)](D''_{C(j)})$}
      \EndFor
    \EndWhile
    \State \Return $M$
  \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
  \caption{ Learning a discrete-valued Bayesian network}
  \label{alg:structure_learn}
  \begin{algorithmic}[5]
  \Function{Learn\_DBN}{$D''$, $C$, $order$, $u_{parent}$, $C$, $u_{cycle}$}
    \State $n \leftarrow$ the number of variables in the Bayesian network
    \State $k \leftarrow median\{ \|v\|, v\notin C\}$
    \State $M[i] \leftarrow$ the discretization policy for the $i$th variable
    \State $D^*_i \leftarrow M[i] (D_i)$, list of samples $D_i$ discretized according to $M[i]$
    \State $D^* \leftarrow $ the discretized data for all variables, where $D^*_i \leftarrow D''_i$ if $i \notin C$
    \State $G \leftarrow$ the initial edgeless graph structure
    \For {$i = 1$ to $n$}
      \If {$i \in C$}
        \State $M[i] \leftarrow$  equal-width discretization with $k$ intervals
        \State $D^*_i \leftarrow  M[i] (D''_i)$
      \EndIf
    \EndFor
    \For {$i =1$ to $n$}
      \State $P_{old} \leftarrow f(X^*_i,\Pi_{X^*_i})$: Equation \ref{eq:f_x_p}
      \State OKToProceed $\leftarrow$ \textbf{true}
      \While {OKToProceed \textbf{and} $\|\Pi_{X^*_i}\| < u_{parent}$}
        \State $Y \leftarrow$ an element from the set $order[1:i] \backslash \Pi_X$
        \State $P_{new} \leftarrow f(X^*_i,\Pi_{X^*_i} \cup Y)$
        \If {$P_{new} > P_{old}$}
          \State $P_{old} \leftarrow P_{new}$
          \State $\Pi_{X_i} \leftarrow \Pi_{X_i} \cup Y $
          \State $M \leftarrow$ {DISCRETIZE}({$D''$, $G$, $C$, $u_{cycle}$}): Algorithm \ref{alg:disc_two}
          \State $D* = M(D'')$
        \Else
          \State OKToProceed $\leftarrow$ \textbf{false}
        \EndIf
      \EndWhile
    \EndFor
    \State \Return $G$, $M$
  \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

\subsection{Auto MPG Dataset}
\label{subsec:auto}

In this subsection, two experiments are conducted on the Auto MPG dataset from the Irvine repository \citep{Lichman_2013}. The dataset has \num{392} instances after deleting the six instances with missing data, and eight variables. Three variables are discrete: $B$, $G$, and $H$ with cardinality 5, 13, and 3 respectively. Two expiriments are conducted, one with a given network structure and one in which the structure is learned.

\subsubsection{Experiment 1 on the Auto MPG dataset}
\label{subsubsec:auto_exp1}

@@

Figure \ref{fig:auto_exp1_distr_1_3} compares the discretization result on continuous variables $A$ and $C$ with the raw data of Auto MPG data set. The color of discretized area shows the probability of a sample being in the discretized area. The black dots in Figure \ref{fig:auto_exp1_distr_1_3} demonstrate the distribution of the raw data. As shown in the figure, the discretization edges and the resulting marginalized probability match the raw data well.

@@

\subsubsection{Experiment 2 on the Auto MPG dataset}
\label{subsubsec:auto_exp2}

@@

Figure \ref{fig:auto_exp2_distr_1_3} compares the edges of the learned network in Figure \ref{fig:auto_graph_2} with the raw data on variables $A$ and $C$. Again, the black dots are raw data points. Although the numbers of discretization edges of $A$ and $C$ shown in Figure \ref{fig:auto_graph_2} are less than Table \ref{table:auto_disc_table_1}, they still have a good capture of raw data distribution.

@@

In this subsection, another two experiments are conducted on the Wine dataset from the Irvine repository \citep{Lichman_2013}. This dataset has 178 instances and 14 variables. Only variable $A$ is discrete-valued with cardinality number 3. Again, in the first experiment, the network structure is given. In the second experiment, the network structure is not provided.

@@

The Bayesian network in Figure \ref{fig:wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 1000 times. Table \ref{table:wine_disc_table_1} shows a comparison between the proposed method and the MDL principle discretization method. The proposed method is still better than MDL principle discretization in terms of likelihood, although the latter returns non-trivial result in this experiment. Note that the proposed method with the approximation has more intervals after discretization, and it has a slightly better result in terms of likelihood. However, the improvement is marginally small, which indicates that the proposed method without the approximation captures good enough discretization result even if the numbers of intervals after discretization are smaller. In addition, as shown in next dataset, the approximation might cut continuous variables into too many intervals. Therefore, the proposed method without the approximation should be still considered a better approach.

\begin{figure}[ht]
\centering
    \begin{tabular}{cc}
      \input{graph_wine_1}
    \end{tabular}
  \caption{K2 structure learning with prediscretization on the Wine dataset}
  \label{fig:wine_graph_1}
\end{figure}

\begin{table}
\centering
\scalebox{1.0}{
\input{table_wine_1.tex}
}
\caption{Discretization result of Wine dataset based on the graph Fig. \ref{fig:wine_graph_1}}
\label{table:wine_disc_table_1}
\end{table}

@@

Figure \ref{fig:wine_exp2_distr} shows the discretization result on variable $E$ and $K$. The discretization edge on variable $E$ is same as the edge found by the MDL principle and the proposed method in Figure \ref{fig:wine_exp1_distr}. This indicates that some discretization edges are robust against the network structure.

@@

In this subsection, another two experiments are conducted on the Housing dataset from the Irvine repository \citep{Lichman_2013}. This dataset has 506 instances and 14 variables. Only variables $D$ and $I$ are discrete-valued with cardinality numbers 2 and 9, respectively. Again, in the first experiment, the network structure is given. In the second experiment, the network structure is not provided.

\subsubsection{Experiment 1 on the Housing dataset}
\label{subsubsec:housing_exp1}

The Bayesian network structure in Figure \ref{fig:housing_graph_1} is obtained by prediscretizing each continuous variable into five uniform-width intervals, then running the K2 algorithm one thousands time and choosing the network with the highest K2 score. Table \ref{table:housing_disc_table_1} shows the numbers of intervals after discretization on each continuous variables. MDL method does not discretize most variables. The proposed method with the approximation discretizes variables into too many intervals. For example, it discretized $J$ into 58 intervals. The proposed method without the approximation has a good control of number of intervals.
\begin{figure}[ht]
\centering
    \begin{tabular}{cc}
      \input{graph_housing_1}
    \end{tabular}
  \caption{K2 structure learning with prediscretization on Housing dataset}
  \label{fig:housing_graph_1}
\end{figure}

\begin{table}
\centering
\scalebox{1.0}{
\input{table_housing_1.tex}
}
\caption{Discretization result of Housing dataset based on the graph Fig. \ref{fig:housing_graph_1}}
\label{table:housing_disc_table_1}
\end{table}

Figure \ref{fig:housing_exp1_distr_3_5} and Figure \ref{fig:housing_exp1_distr_8_5} show the discretization result by the propose method on the network in Figure \ref{fig:housing_graph_1}. In Figure \ref{fig:housing_exp1_distr_3_5}, the scatter points, which stands for the raw data, has been jittered, since there are many repeated values in the raw data on the variable pair $C$ and $E$. These repeating values cause the high number of intervals after discretization for both $C$ and $E$, because in some sense, each repeated-value point form a single discretized area. On the other hand, there is no such over-repeated values of the raw data on variable $H$. Thus, the numbers of intervals after discretization for variable $E$ remains normal, as what we have seen in previous datasets.

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_housing_exp1_distr_3_5}
    \end{tabular}
  \caption{The discretization result on variable $C$ and $E$ of the network in Figure \ref{fig:housing_graph_1}}
  \label{fig:housing_exp1_distr_3_5}
\end{figure}

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_housing_exp1_distr_8_5}
    \end{tabular}
  \caption{The discretization result on variable $H$ and $E$ of the network in Figure \ref{fig:housing_graph_1}}
  \label{fig:housing_exp1_distr_8_5}
\end{figure}

\subsubsection{Experiment 2 on the Housing dataset}
\label{subsubsec:housing_exp2}

Figure \ref{fig:housing_graph_2} is the learned discrete-valued Bayesian network from the Housing dataset by running Algorithm \ref{alg:structure_learn} 50 times. In both Figure \ref{fig:housing_graph_1} and Figure \ref{fig:housing_graph_2}, the variable $D$ is not connected to any other variable. Continuous variables $C$, $E$, $J$ and $K$, which are all in a Markov blanket, have high cardinality numbers after discretization. This is reasonable, since when discretizing one variable, the expected cardinality is close to highest cardinality number in the Markov blanket. This will lead to a group of variables that are close to each other and all have high cardinalities.

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_housing_2}
    \end{tabular}
  \caption{The learned discrete-valued Bayesian network from the Housing dataset}
  \label{fig:housing_graph_2}
\end{figure}

Figure \ref{fig:housing_exp2_distr_3_5} and Figure \ref{fig:housing_exp2_distr_8_5} show the discretization result on variables of the network in Figure \ref{fig:housing_graph_2}. Again, variable $C$ and $E$ have many discretization edges due to the repeated values. Although the number of intervals after discretization on $H$ is not big, it captures the distribution of the raw data along with the discretization edges on $E$.

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_housing_exp2_distr_3_5}
    \end{tabular}
  \caption{The discretization result on variable $C$ and $E$ of the network in Figure \ref{fig:housing_graph_2}}
  \label{fig:housing_exp2_distr_3_5}
\end{figure}

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_housing_exp2_distr_8_5}
    \end{tabular}
  \caption{The discretization result on variable $H$ and $G$ of the network in Figure \ref{fig:housing_graph_2}}
  \label{fig:housing_exp2_distr_8_5}
\end{figure}
